Labeling Calculations

### 2022-11-02 99_labeling_calculations.Rmd
required incubation times

```{r setup, include=FALSE}
# libraries
library(tidyverse)
library(lubridate)
library(latex2exp)
library(isotopia) # install.packages("devtools"); devtools::install_github("sebkopf/isotopia")

@@

@@

```{r "enrichment_curves_zoomed2", fig.width = 8 , fig.height = 7, warning=FALSE, message=FALSE}
p1 + coord_cartesian(ylim = c(0.01, 0.025))
```

>>>>

```{r setup, include=FALSE}
# libraries
library(tidyverse)
library(lubridate)
library(latex2exp)
library(isotopia) # install.packages("devtools"); devtools::install_github("isoverse/isotopia")

@@

```{r}
# plot
inc_times %>% 
  # spread the different F_t_type values
  select(-F_t.percent, -inc_time.s) %>%  spread(F_t_type, inc_time.log10) %>% 
  # color factor
  mutate(label_strength = paste("F_L =", F_L.percent, "at%") %>% factor() %>% fct_inorder()) %>% 
  # send to plot
  ggplot() +
  aes(
    gen_time.log10, 
    color = label_strength, 
    fill = label_strength
    ) + 
  geom_ribbon(
    mapping = aes(ymin = min, ymax = max), 
    alpha = 0.1
    ) +
  geom_line(
    mapping = aes(y = average), 
    size = 2) +  
  labs(title =
         sprintf("Required incubation times to reach enrichment\nbetween %.0f\u2030 and %.0f\u2030 (thick line = %.0f\u2030)",
                 dD_enrich_min, dD_enrich_max, dD_enrich_avg),
       linetype = "target incubation times") +
  scale_x_continuous(
    "generation time", 
    breaks = gen_times$gen_time.log10,
    labels = function(x) gen_times$label,
    expand = c(0, 0)
  ) +
  scale_y_continuous(
    "required incubation time",
    breaks = y_breaks$inc_time.log10,
    labels = function(x) y_breaks$label,
    expand = c(0, 0)
  ) +
  scale_color_brewer("tracer strength", palette = "Set1") +
  scale_fill_brewer("tracer strength", palette = "Set1") +
  coord_cartesian(ylim = range(y_breaks$inc_time.log10)) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 12),
        axis.text.y = element_text(size = 12),
        axis.title = element_blank(),
        panel.grid.minor = element_blank())
```

@@

```{r "enrichment_curves_zoomed2", fig.width = 8 , fig.height = 7, warning=FALSE, message=FALSE}
p1 + coord_cartesian(ylim = c(0.01, 0.025), xlim = c(0, 300))
```
